GEE models

### 2017-10-16 doc/esm.Rmd
rearranged setup code chunks in esm

```{r setup, include=FALSE}
devtools::load_all()
set_options()
```

```{r captions}
# Include captions below using `captioner` package via library(captioner)
stab <- captioner::captioner(prefix = 'ESM Table')
cite_st <- pryr::partial(stab, display = 'cite')

@@

```{r setup, include=FALSE}
devtools::load_all()
set_options()
knitr::opts_chunk$set(dev = "png")

>>>>

```{r tab-captions}
# Include captions below using `captioner` package via library(captioner)
knitr::opts_chunk$set(results = "markup")
stab <- captioner::captioner(prefix = 'ESM Table')
cite_st <- pryr::partial(stab, display = 'cite')

@@

```{r fig-captions, include=FALSE}
knitr::opts_chunk$set(dev = "png")
